\documentclass[11pt]{article}
\usepackage{times}
\usepackage{enumerate}

\begin{document}
\section{Meeting Aug 6th}
\subsection{Thesis Improvement}
\begin{enumerate}
\item  Write example for all the features.
\item Include global statistics  for verb categories.
\item Standard description for the Logistic Regression Algorithm. Examples: Adwait Ratnaparkhi, Hastie and Tribshrani
\item Properties of the datasets used with examples.
\item Broaden the Discussion Elements section.
\item Error Analysis Include more examples.
\item Include Related Work Section.
\item Introduce the problem based on older papers when the problem was introduced.
\item Include some Math.
\end{enumerate}

\section{Meeting Aug 30th}
\subsection{Classifier Discussion}
\begin{enumerate}
\item  Decide some features based on the Syntactic Pattern.
\item Reading: Ripper, Induction Logic Programming, William Cohen...
\item Reading: Fast Text (Mikolov)
\item Use Dan Roth's training and testing set configuration.
\item Model the classifier using a decision tree using Syntactic Patterns in hierarchical way.
\item Complete Comma Simplification before the next meeting i.e. Weekend.
\end{enumerate}

\section{Meeting Sep 3rd}
\subsection{FastText and Features Discussion}
\begin{enumerate}
\item Implement FastText for Syntactic Patterns to predict mearest syntactic patterns.
\item Select Unigram, Bigram and TriGram or ngram features based on the frequency they occur in the training data.
\item Select some positional features.
\item Prepare 1000 questions for training data.
\item Try this experiment with LR and LR with Regularizer.
\end{enumerate}

\section{Meeting Sep 19th}
\subsection{Niyati joins the team!}
\subsection{Sentence Simplification}
\begin{enumerate}
\item Sentence Simplification should be done by next meeting.
\end{enumerate}
\subsection{ScienceIE Eval}
\begin{enumerate}
\item{Understand the problem well! and prepare some discussion about the approach we may take}
\end{enumerate}
\end{document}